Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-28 paper.tex
Added 5 (Conclusion) and 6 (Outlook)

TODO: Zusammen am Schluss

@@

TODO: Zusammen am Schluss

>>>>

In this paper, we describe an architecture for a novel and feature-rich DaaS that is, by principle, superior to comparable products and approaches because it supports running unmodified Linux and Windows applications. Furthermore, we identified characteristic issues -- concerning compatibility, performance, stability, and usability -- during the development and implementation of our DaaS and present solutions to overcome these challenges.

@@

For future work, we plan to do a performance analysis that includes an evaluation of different user behaviors for various popular applications and realistic deployment and utilization scenarios.
